---
title: "Chemical Evaluation"
author: "Yuehan Xiao & Xu Xu"
date: "3/17/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

``````{r include=FALSE, cache=FALSE}

library(tidyverse)
library(readxl)

```




##28 Unique Chemical

```{r, echo=FALSE,message=FALSE, warning=FALSE}
veg.1 <- read_xlsx("veg1.xlsx")
c <- apply(veg.1, 2, n_distinct)
c <- c[c>1]
d <- names(c[c==1])
e <- names(c[c>1])
veg.2 <- select(veg.1, e)
cnames.2 <- colnames(veg.2)

veg.3 <- dplyr::rename(veg.2, 
                       Geo = `Geo Level`, 
                       State = `State ANSI`,
                       Data = `Data Item`,
                       Category = `Domain Category`)

cnames.3 <- colnames(veg.3)


yy <- separate(veg.3, Category, into = c("label", "quant"), sep=",")
ru <- filter(yy, label=="RESTRICTED USE CHEMICAL")

ru1 <- ru %>% select(label, quant) %>% unique()
print(ru1, n=7)

```
Initially, we select 28 unique restricted used chemicals in order to find their corresponding cas codes and LD50 values (filtering by species-rat, study type-oral and averaging the toxicity value)

##LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
Toxicity<-read_xlsx("Toxicity_Tidy_Table.xlsx")
print(Toxicity, n=2)

```
There are total 63 observations and 9 variables in the clean1 data frame.We seperate 5 methods into 5 column. A represents " APPLICATIONS, MEASURED IN LB"; B represents " APPLICATIONS, MEASURED IN LB / ACRE / APPLICATION, AVG" ; C represents " APPLICATIONS, MEASURED IN LB / ACRE / YEAR, AVG"; D represents " APPLICATIONS, MEASURED IN NUMBER, AVG"; E represents " TREATED, MEASURED IN PCT OF AREA PLANTED, AVG". Additionly, we add a column of LD50 which includes the LD50 values for corresponding chemicals.The Toxicity data frame is the new complete tidy data frame.


##Method A (APPLICATIONS, MEASURED IN LB) Value Versus LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
plot(Toxicity$LD50, Toxicity$A)
```

##Method B (APPLICATIONS, MEASURED IN LB / ACRE / APPLICATION, AVG) Value Versus LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
plot(Toxicity$LD50, Toxicity$B)
```

##Method C (APPLICATIONS, MEASURED IN LB / ACRE / YEAR, AVG) Value Versus LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
plot(Toxicity$LD50, Toxicity$C)
```

##Method D (APPLICATIONS, MEASURED IN NUMBER, AVG) Value Versus LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
plot(Toxicity$LD50, Toxicity$D)
```

##Method E (TREATED, MEASURED IN PCT OF AREA PLANTED, AVG) Value Versus LD50 
```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.height=4, fig.width=8}
plot(Toxicity$LD50, Toxicity$E)
```
## Relationship Between Chemical Usage and LD50
Chemical Usages and LD50 doesn't have a strong relationship. This is predictable because LD50 represents the amount of a toxic agent that is sufficient to kill 50 percent of a population of animal within a certain time compare to Chemical Usage, which refers to the average number of pounds of pesticide active ingredient applied to an acre of land. However, through plots, it might indicate that the higher the LD50 the lower the Chemical Usage but this still needs further investigation.  
