---
title: "Weather station 46035"
author: "Yuehan Xiao & XuXu"
date: "3/15/2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

``````{r include=FALSE, cache=FALSE}

library(tidyverse)
library(tidyr)
library(stringr)
library(dplyr)
library(plyr)

```


##Premise

Since all air temperature and water temperature information for 2012 are recorded as 999.0, which means that these information we want are missing, so we no longer consider 2012 in our investigation. We can't find record of year 2013 from the website, so we decide to skip it. It's unable to read 2000's table, so we don't use this year. Therefore, we use the data from 1985 to 2017 except year 2000, 2012, 2013 to compute the time series.

##Air Temperature's Time Series Plot

```{r, echo=FALSE}


# combined all the cleaned data into a csv file
wholedata<-read.csv("wholedata.csv")
wholedata <-wholedata[,-1]
wholedata <- wholedata[-c(3625, 4420, 4421), ]

#ATMP
whole_data_ATMP <- wholedata[1:3]
whole_data_ATMP <- whole_data_ATMP<-spread(whole_data_ATMP, key = MM_DD, value = ATMP)


#Air temperature Time series plot
row.names(whole_data_ATMP) <- whole_data_ATMP[,1]
whole_data_ATMP<-whole_data_ATMP[,-1]
ts1 <- as.vector(t(whole_data_ATMP[,-1]))
ts2 <- ts(rev(ts1), start= c(1985,1), end=c(2017,12),frequency=12)
ts3 <- ts.plot(ts2, gpars=list(xlab="year", ylab="Air_Temperature", lty=c(1:3)),col='purple')
```

##Water Temperature Time Series Plot

``````{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
#WTMP
whole_data_WTMP <- cbind(wholedata[1:2], wholedata[4])
whole_data_WTMP <- whole_data_WTMP<-spread(whole_data_WTMP, key = MM_DD, value = WTMP)

#Water temperature Time series plot
row.names(whole_data_WTMP) <- whole_data_WTMP[,1]
whole_data_WTMP<-whole_data_WTMP[,-1]
ts4 <- as.vector(t(whole_data_WTMP[,-1]))
ts5 <- ts(rev(ts4), start= c(1985,1), end=c(2017,12),frequency=12)
ts6 <- ts.plot(ts5, gpars=list(xlab="year", ylab="Water_Temperature", lty=c(1:3)),col='blue')
```

## Plot Between Water Temperature and Air Temperature

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=wholedata) +
  geom_smooth(mapping = aes(x=ATMP, y=WTMP))
```

According to the plot, there is a positive relationship between air temperature and water temperature.

##Significance Test on Temperature Change 
For both water mean temperature and air mean temperature, we decided to use the linear regression to compare the mean temperature change over 30 years. Since the comparison is over 30 years, we could not simply do a pairwise t-test to compare the change of the mean. 

##Significance on Water Temperature Change over 30 years

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=10)}
wholedata_WTMP_Linear <- cbind(wholedata[1:2], wholedata[4])
WTMP_Linear<- lm(WTMP ~  YYYY,data=wholedata_WTMP_Linear)
plot(WTMP ~ YYYY, data=wholedata_WTMP_Linear)
abline(lm(wholedata_WTMP_Linear$WTMP~wholedata_WTMP_Linear$YYYY))
```

##Water Temperature Part 2

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=10)}
summary(WTMP_Linear)
```
Since p value is smaller than 2.2e-16, which is smaller than alpha 0.05, so the change of the mean water temperature over past 30 years is significant.



##Significance on Air Temperature Change over 30 years

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=10)}
wholedata_ATMP_Linear <- cbind(wholedata[1:3])
ATMP_Linear <- lm(ATMP~YYYY, data=wholedata_ATMP_Linear)
plot(ATMP~YYYY, data=wholedata_ATMP_Linear)
abline(lm(wholedata_ATMP_Linear$ATMP~wholedata_ATMP_Linear$YYYY))
```

##Air Temperature Part 2

```{r, tidy=TRUE, tidy.opts=list(width.cutoff=10)}
summary(ATMP_Linear)
```
Since the p value is smaller than 2.2e-16, which is smaller than alpha 0.05, so the change of the mean air temperature over past 30 years is significant.

## Influence of the Sampling 

Whether our sampling of choosing one sample per day affects our evaluation of temperature change or not depends on the trend of the temperature within this specific area. If the temperature over the whole day is moderately stable,we can approxiamately regard the temperature at 12pm at each single day as the average temperature over the whole day. In this case, the sampling method does not affect our evaluation of temperature change much. However, if there exists large varaitions in temperature over the whole day, the temperature at 12pm can not be regarded as a reasonable respresentation of the average temperature of each single day. In this case,our sampling method affects the evaluation of temperature change a lot.
